The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables

### 2015-04-08 draft.tex
wording

The emission measure of a plasma is directly proportional to its density.
The simplest way to simultaneously affect the density in the wind (for fixed mass loss rate),
as well as the velocity gradients, is by modifying the poloidal velocity
law. Therefore, we focus on just two kinematic variables (section~\ref{kinematics}):

@@

This revised model demonstrates that one can achieve a more
realistic optical spectrum by altering just two kinematic parameters. 
However, it may also be possible to achieve this by modifying
other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
inner and outer launch radii. For example, increasing the mass loss rate of the wind
increases the amount of recombination emission (which scales as $\rho^2$), 
as well as lowering the ionization parameter and increasing optical depth through the wind. 
Larger launching radii and covering factors tend to lead to a larger emitting volume, 
but this is moderated by a decrease in density 
for a fixed mass-loss rate. We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
affects the emergent UV spectrum seen at inclinations $<\theta_{min}$ as 
the inner disk is uncovered. This causes less absorption in the UV resonance lines,
but the effect on the optical spectrum is negligible.
We have verified this general behaviour, but
we suggest that future work should investigate the effect of these parameters in more detail,
as well as incorporating a treatment of clumping.
If a wind really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
understanding the true mass loss rate and geometry of the outflow is clearly important.

>>>>

The emission measure of a plasma is directly proportional to its density.
The simplest way to simultaneously affect the density in the wind (for fixed mass-loss rate),
as well as the velocity gradients, is by modifying the poloidal velocity
law. Therefore, we focus on just two kinematic variables (section~\ref{kinematics}):

@@

This revised model demonstrates that one can achieve a more
realistic optical spectrum by altering just two kinematic parameters. 
However, it may also be possible to achieve this by modifying
other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
inner and outer launch radii. For example, increasing the mass-loss rate of the wind
increases the amount of recombination emission (which scales as $\rho^2$), 
as well as lowering the ionization parameter and increasing the optical depth through the wind. 
Larger launching regions and covering factors tend to lead to a larger emitting volume, 
but this is moderated by a decrease in density 
for a fixed mass-loss rate. We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
affects the emergent UV spectrum seen at inclinations $<\theta_{min}$ as 
the inner disk is uncovered. This causes less absorption in the UV resonance lines,
but the effect on the optical spectrum is negligible.
We have verified this general behaviour, but
we suggest that future work should investigate the effect of these parameters in more detail,
as well as incorporating a treatment of clumping.
If a wind really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
understanding the true mass-loss rate and geometry of the outflow is clearly important.
